\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly -- The Domino Experiment

### 2014-09-16 paper.tex
2nd pass

\textbf{Engagement} is a metric that has been extensively used and studied both
in HRI and during interactions with other agent-like systems. It has been
defined from several perspectives. For example \cite{sidner_where_2004} define
engagement as \textit{``the process by which two (or more) participants
establish, maintain and end their perceived connections''}. A definition of
long-term engagement is proposed by \cite{bickmore_maintaining_2010}:
\textit{``the degree of involvement a user chooses to have with a system over
time''}.

@@

@@

    \item The robot gets \textbf{lost}: When called by the child to come over,
    the robot goes wrong, without any observable reason, and remains at the
    wrong location. We expect this to be perceived as a bug or system error
    which causes the robot to not work correctly, and hypothesize decreased
    attributions of human-likeness to the robot.

    \item The robot \textbf{disobey}: When called by the child to come over, the
    robot shows it refuses to obey by literally ``shaking its head'' and
    becoming red. The robot then goes to a wrong location and remains there
    while it continues to shake its head. We expect the disobey behaviour to be
    perceived as the robot having an \textit{``own will''}, and we assume this
    leads to increased attributions of human-likeness (ascribing intentionality)
    to the robot.

@@

The robot was controlled by a human wizard, who was in the same room (see
Figure~\ref{fig:domino-setup}). This was to ensure that the wizard could see
children's interaction and hear their commands to the robot without any delay.
Only one group asked at the beginning of the experiment if the wizard was the
one actually controlling the robot. This did not seem to subsequently influence
their behaviour.

@@

\subsubsection{The Ranger robot}

@@

In our study, there were a total of 14 runs, and at each run, the robot exhibits
one out of four possible behaviours: \emph{correct}, \emph{mistake}, \emph{lost}
or \emph{disobey}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
showed one of the misbehaviour (\emph{mistake}, \emph{lost} or \emph{disobey})
at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
(see Figure~\ref{fig:domino-time-active}). The study is build as a
between-subject study, and the type of misbehaviour was therefore always the
same for a given group.

@@

\begin{figure}[!t]
    \centering
    \subfloat[mistake]{
        \label{fig:domino-mistake}
        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
    }
    \subfloat[lost]{
        \label{fig:domino-lost}
        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
    }
    \subfloat[disobey]{
        \label{fig:domino-disobey}
        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
    }
    \caption{\small The three robot misbehaviours.}
    \label{fig:domino-misbehaviour}
\end{figure}

@@

During the misbehaving runs, the robot's behaviour is manipulated in three
possible ways:

@@

\subsubsection{Perception: semi-structured interviews}

@@

\subsection{Manipulation check: Negligible impact of the conditions}

As stated in the introduction, we had hypothesized that the \textit{disobey}
behaviour is perceived as the robot intentionally not doing what it should do.
The \textit{mistake} behaviour was intended to show that the robot can do a
mistake but is aware of it and able to repair its mistake, which should also
lead to some perception of intentionality.  Contrary, we expected that the
\textit{lost} condition is perceived as a malfunction or bug of the robot.  In
the second interview, after the robot had misbehaved, we asked children whether
the robot always did what they wanted it to do. Most children disagreed and said
they noticed something strange. However, there were some children who gave a
positive answer, suggesting that they found the robot always did what they
wanted it to do. This was a surprise. Had they not noticed the robot's
misbehaviour? Why not? On one hand, we found that children sometimes gave
contradictory replies when asked the same question twice. This is difficult to
interpret. On the other hand, children may have a general tendency to please
adults \cite{leite_long-term_2013}, and it could be the case that some were too
shy to tell us that the robot did something strange.

@@

We nevertheless asked children why they thought the robot had not always come
over to them. 4 of the children did not reply. The remaining ones gave a variety
of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
is doing and that it could go \textit{no matter where}\footnote{We translated
children's answers from French to English. For some expressions the meaning
and connotation of an expression may not be the same. We understand
\textit{``partir dans tous les sens''} as ``to go off in all possible
directions'' and hence interpret this reflects viewing the robot as being
unpredictable.} because \textit{``with robots you have these kind of problems,
they do no matter what''}. 8 replies concerned \textit{technical problems}
(including \textit{broken parts}), suggesting that children perceived the
misbehaviour as unintended by the robot. 2 of the children who had interacted
with the disobeying robot said Ranger was \textit{angry}, which none of the
children in other conditions replied. Several children ascribed intentionality
to Ranger explaining that it \textit{did not want to continue} carrying domino
tiles or that it \textit{made a mistake / did something silly}\footnote{We
understood \textit{``faire une bêtise''} as ``to do a silly thing'' in the sense
of making a mistake.}.

@@

In our case, it is not easy to make a clear statement about how each of the
manipulations was perceived by the children.  Similar to how people reacted to
the cheating robot in the study of \cite{short_no_2010}, most children showed
surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
two boys tended to shout to the robot after it had disobeyed). The
\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
negative implication: later three of the children in this condition stated they
would not accept Ranger as a friend \textit{because it did not always come over
when they asked it to come over}. \cite{short_no_2010} described a similar
implication of the robot cheating behaviour: participants made unfavorable
character attributions to the cheating robot, so the robot's actions affected
perceptions of the robot as ``fair'' and ``honest''.

@@

\subsection{Engagement}

@@

Overall, was there an effect on engagement when the robot misbehaved? We compare
children's engagement during the interaction phase with the expected robot
behaviour and during the interaction phase with the unexpectedly behaving robot.
A statistical analysis revealed a significant difference between the average of
engagement actions carried out during the first 7 runs (correct robot behaviour)
and during the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1,
p=.03). In all three conditions, children carried out more engagement
actions with the unexpectedly behaving robot. No interaction effect was found
between the two phases of interaction (expected / unexpected) and condition
(F(2,36)=1.2, p=.31). In general, this finding supports our first hypothesis:
children show more engagement toward a robot that behaves unexpectedly from time
to time compared to a robot that always behaves correctly.

@@

        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
        \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
        \bottomrule
    \end{tabular}
    \caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The
    \textit{lost} robot elicits the highest index, which suggests that it is
    anthropomorphized more. Contrary to our hypothesis, data suggests that the
    \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot
    more.}

@@

Our data on the anthropomorphism index also suggest \textbf{qualitative gender
differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
more with the robot than girls; though not significantly. This is
counter-intuitive concerning the negative correlation between amount of
interaction with the robot and anthropomorphism tendency.) It would be
interesting to investigate in more detail whether boys are more prone to
anthropomophize a robot than girls.\footnote{Findings presented in
\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
study, males tended to think of the robot as more human-like and accordingly
showed more ``social facilitation'' than females, who perceived the robot as
more machine-like.}

\paragraph{Summary}

The established \textit{anthropomorphism index} suggests that children tend to
conditionally anthropomorphize the robot. Higher indexes of anthropomorphism
were found in the \textit{lost} and \textit{mistake} condition which was against
our hypothesis. Interestingly, data suggests a significant negative correlation
of engagement and anthropomorphism index. It appears that groups who interacted
more with the robot perceived it as less-humanlike. This raises the question to
what extent anthropomorphic perceptions of a robot can last over time, and with
increasing interaction experience.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lessons Learned and Future Directions}

We found that in a playful scenario where 4-5 year old children play domino
together with a robot, the robot seems to be more engaging when it shows some
misbehaviour compared to when it always behaves as expected. However, we
cannot say if this effect holds also after novelty has worn off.

From what we
have seen in the Domino Study, we have a rough estimate of how children react
and relate to a robot that behaves unexpectedly from time to time. They are
mostly surprised, laugh at the robot, and they tend to be more engaged and
playful. However, they are also confused and cannot really make sense of the
robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
the unexpected robot behaviour entirely as a malfunction (something that happens
to a machine) or as being intended and based on a motivation (something related
to a social entity). Children stated both, when asked why the robot had
misbehaved. Some referred to \textit{``a technical problem''} while others said
the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
tiles any more but rather go on a tour outside''}. Maybe our manipulations were
not as clearly designed as we expected. There is always some freedom in how
things are interpreted -- especially with young children.  Certainly more work
needs to be done to investigate which robot behaviour is most beneficial for
young children and can promote their engagement and motivation to interact with
Ranger over extended periods of time.

@@

\subsection{Limitations}

This study and the results have several limitations.  First, we did not have a
real control group in which the robot always behaved correctly. Instead, we took
the first interaction phase as a reference for how children interact with the
correctly behaving robot.  Also, the sample size of 13 groups was small. There
were  variations in the data due to the individual differences of children. More
data could have allowed for a better comparison between the conditions.

With the manipulation of the robot behaviour we were able to surprise children.
However, it is questionable how often the same type of behaviour manipulation
leads to surprise. Moreover, our experiment was a short-term interaction study
while we try to make statements about how to sustain long-term engagement. This
is critical but not unusual. Long-term HRI studies with young children are
extremely rare as they are difficult to set up as well as time and resource
consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
improved our study by setting up several short interaction sessions spreading
over several weeks. At the end of each session we could have asked whether
children want to play again with the robot. Such a study could have helped to
investigate the long-term interaction with the robot and the impact of the
behavioural variances.

\subsection{Lessons Learned}

One of the lessons learned is that it is difficult to set up a controlled lab
study with young children. Children are not like adults who patiently
participate in a 45-minutes experiment and then get some reward in the end. On
one hand, an experiment with children should not be boring for them, but on the
other hand, you would like to seriously collect some data. A lot of the
challenges we experienced are also described in \cite{ros_child-robot_2011}. One
of the most difficult parts turned out to be the interviews with the children.
We need to be careful to not over interpret some of their answers. Some children
seem to not have a clear opinion and partly contradict themselves. These answers
are not easy to interpret. An interview script including the questions need to
be designed very carefully, and should definitely be tested beforehand with the
respective age group.

Overall, it appears that when trying to study something in more detail, such as
the manipulation of robot behaviour, 4-5 year old children may be too young. But
when trying to evaluate a more general approach, the design of a prototype, or
an interaction scenario, children are a very good choice. They say things as
they are and react very naturally, when compared to adults, who may reply more
socially desired.

\paragraph{Summary}

In this study, we investigated the effect of unexpected robot behaviour on
children's engagement in interacting with Ranger and on their perception of the
robot.  Our first hypothesis finds support: children show more engagement toward
a robot that behaves unexpectedly from time to time. Further, different types of
unexpected behaviour may have a different effect, and therefore the behaviour
manipulation needs to be designed with care.
We did not find support for our second hypothesis which stated that children
perceive a robot showing intention or cognitive abilities as more human-like
than a robot that appears to have a system error. This may be due to the study
setup and the fact that children did not interpret the robot misbehaviour in the
conceived way. Our findings seem to suggest the contrary to our hypothesis. A
robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
anthropomorphized than a robot that \textit{disobeyed}. But again, as children
may have misinterpreted these robot behaviours we cannot be sure about this
result.

Another outcome of this study is the initial development and first tryout of an
\textbf{anthropomorphism index}. This index considers both behavioural and
perception aspects and is able to indicate lower and higher levels of
anthropomorphism along this continuous index. At the moment, there is no such
index available that quantifies anthropomorphism along a scale and there is no
technique that combines behaviour and perception. In the future, we will need to refine
and improve this scale. For instance, we need to identify the specific factors
that should be included as measurement points in such a scale, for both aspects
(behaviour and perception). Also, we need to think about how to balance the two
aspects appropriately. Probably, also characteristics of the person, the robot,
and the situation need to be considered.

>>>>

\emph{Engagement} is a metric that has been extensively used and studied both
in HRI and during interactions with other agent-like systems. It has been
defined from several perspectives. For example \cite{sidner_where_2004} define
engagement as \textit{``the process by which two (or more) participants
establish, maintain and end their perceived connections''}. A definition of
long-term engagement is proposed by \cite{bickmore_maintaining_2010}:
\textit{``the degree of involvement a user chooses to have with a system over
time''}.

@@

    \item The robot gets \textbf{lost}: When called by the child to come over,
        the robot goes wrong, without any observable reason, and remains at the
        wrong location. We expect this to be perceived as a mechanical
        malfunction (a bug or system error which causes the robot to not work
        correctly), and hypothesize decreased attributions of human-likeness to
        the robot.

    \item The robot \textbf{disobey}: When called by the child to come over, the
        robot shows it refuses to obey by literally ``shaking its head'' and
        becoming red. The robot then goes to a wrong location and remains there
        while it continues to shake its head. We expect the disobey behaviour to
        be perceived as the robot having an explicit \textit{``own will''}, and
        we assume this leads to increased attributions of human-likeness
        (ascribing intentionality) to the robot.

@@

@@

The Ranger~\cite{mondada2014ranger} is a wheeled box (27 x 37 x 37 cm) with
partial wooden surface. Being remote controlled, it can move around a flat
surface, move its eyes and eyebrows, display colors (LEDs) and light patterns,
and play sounds through Bluetooth speakers.  The robot was controlled by a human
wizard, who was in the same room (see Figure~\ref{fig:domino-setup}). This was
to ensure that the wizard could see children's interaction and hear their
commands to the robot without any delay.  Only one group asked at the beginning
of the experiment if the wizard was the one actually controlling the robot. This
did not seem to subsequently influence their behaviour.

@@

@@

In our study, there were a total of 14 runs, and at each run, the robot exhibits
one out of four possible behaviours: \emph{correct}, \emph{lost}
\emph{disobey} or \emph{mistake}.  The first 5 runs (\emph{1.1} to \emph{1.5}) were used to set
the baseline and the robot always behaved correctly. The children then switched
the roles and in the 9 remaining runs (\emph{2.1} to \emph{2.9}), the robot
showed one of the misbehaviour (\emph{lost}, \emph{disobey} or \emph{mistake})
at the $3^{rd}$ and $4^{th}$ run as well as at the $7^{th}$ and $8^{th}$ run
(see Figure~\ref{fig:domino-time-active}). The study is build as a
between-subject study, and the type of misbehaviour was therefore always the
same for a given group.

@@

\begin{figure}[!t]
    \centering
    \subfloat[lost]{
        \label{fig:domino-lost}
        \includegraphics[width=0.4\columnwidth]{domino-lost.png}
    }
    \subfloat[disobey]{
        \label{fig:domino-disobey}
        \includegraphics[width=0.3\columnwidth]{domino-disobey.png}
    }
    \subfloat[mistake]{
        \label{fig:domino-mistake}
        \includegraphics[width=0.3\columnwidth]{domino-mistake.png}
    }
    \caption{\small The three robot misbehaviours.}
    \label{fig:domino-misbehaviour}
\end{figure}

@@

During the misbehaving runs, the robot's behaviour is manipulated in three
possible ways (Figure~\ref{fig:domino-misbehaviour}):

@@

\subsubsection{Phenomenological perception: semi-structured interviews}

@@

\subsection{Misbehaviour recognition and engagement}

As stated in the introduction, we had hypothesized that the \textit{disobey}
behaviour is perceived as the robot intentionally not doing what it should do.
The \textit{mistake} behaviour was intended to show that the robot can do a
mistake but is aware of it and able to repair its mistake, which should also
lead to the perception of intentionality and introspective skills.  Contrary, we expected that the
\textit{lost} condition is perceived as a malfunction or bug of the robot.  In
the second interview, after the robot had misbehaved, we asked children whether
the robot always did what they wanted it to do. Most children disagreed and said
they noticed something strange.
%However, there were some children who gave a
%positive answer, suggesting that they found the robot always did what they
%wanted it to do. This was a surprise. Had they not noticed the robot's
%misbehaviour? Why not? On one hand, we found that children sometimes gave
%contradictory replies when asked the same question twice. This is difficult to
%interpret. On the other hand, children may have a general tendency to please
%adults \cite{leite_long-term_2013}, and it could be the case that some were too
%shy to tell us that the robot did something strange.

@@

When asked why they thought the robot had not always come
over to them, 4 of the children did not reply. The remaining ones gave a variety
of reasons (Figure~\ref{fig:domino-why-misbehaviour}). The most common answer (9
of 37 replies) was that the robot is somehow \textit{unpredictable} in what it
is doing and that it could go \textit{no matter where}\footnote{We translated
children's answers from French to English. For some expressions the meaning
and connotation of an expression may not be the same. We understand
\textit{``partir dans tous les sens''} as ``to go off in all possible
directions'' and hence interpret this reflects viewing the robot as being
unpredictable.} because \textit{``with robots you have these kind of problems,
they do no matter what''}. 8 replies related to \textit{technical problems}
(including \textit{broken parts}), suggesting that children perceived the
misbehaviour as unintended by the robot. 2 of the children who had interacted
with the disobeying robot said Ranger was \textit{angry}, which none of the
children in other conditions replied. Several children ascribed intentionality
to Ranger explaining that it \textit{did not want to continue} carrying domino
tiles or that it \textit{made a mistake / did something silly}\footnote{We
understood \textit{``faire une bêtise''} as ``to do a silly thing'' in the sense
of making a mistake.}.

@@

%In our case, it is not easy to make a clear statement about how each of the
%manipulations was perceived by the children.  Similar to how people reacted to
%the cheating robot in the study of \cite{short_no_2010}, most children showed
%surprise, were amused, sometimes confused, or occasionally slightly angry (\eg
%two boys tended to shout to the robot after it had disobeyed). The
%\textit{disobeying} robot seemed to evoke the strongest reactions, partly with a
%negative implication: later three of the children in this condition stated they
%would not accept Ranger as a friend \textit{because it did not always come over
%when they asked it to come over}. \cite{short_no_2010} described a similar
%implication of the robot cheating behaviour: participants made unfavorable
%character attributions to the cheating robot, so the robot's actions affected
%perceptions of the robot as ``fair'' and ``honest''.

@@

@@

Overall, we found a significant difference between the average of engagement
actions carried out during the first 7 runs (correct robot behaviour) and during
the second 7 runs, when the robot behaved unexpectedly (F(1,36)=5.1, p=.03). In
all three conditions, children carried out more engagement actions with the
unexpectedly behaving robot. No interaction effect was found between the two
phases of interaction (expected / unexpected) and condition (F(2,36)=1.2,
p=.31). In general, this finding supports our first hypothesis: children show
more engagement toward a robot that behaves unexpectedly from time to time
compared to a robot that always behaves correctly.

@@

        \textit{lost} & \textbf{8.31} & 0.59 & 3 of 4 \\ 
        \textit{disobey} & 6.5 & 3.68 & 2 of 5 \\
        \textit{mistake} & 7.94 & 1.74 & 3 of 4 \\ 
        \bottomrule
    \end{tabular}
    \caption{\textbf{Anthropomorphism index.} The maximum possible index was 16. The
    \textit{lost} robot elicits the highest index, which suggests that it is
    anthropomorphized more. Contrary to our hypothesis, data suggests that the
    \textit{disobeying} robot is anthropomorphized less but the \textit{lost} robot
    more.}

@@

%Our data on the anthropomorphism index also suggest \textbf{qualitative gender
%differences} in children's tendency to anthropomorphize Ranger. Boys (M=8.2,
%SD=3.0) obtained a higher mean index of anthropomorphism than girls (M=6.4,
%SD=2.4). (Interestingly, as it was mentioned before, boys interacted slightly
%more with the robot than girls; though not significantly. This is
%counter-intuitive concerning the negative correlation between amount of
%interaction with the robot and anthropomorphism tendency.) It would be
%interesting to investigate in more detail whether boys are more prone to
%anthropomophize a robot than girls.\footnote{Findings presented in
%\cite{schermerhorn_robot_2008} suggested similar gender differences. In their
%study, males tended to think of the robot as more human-like and accordingly
%showed more ``social facilitation'' than females, who perceived the robot as
%more machine-like.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Directions}

As hypothesised, we found that in a playful scenario where 4-5 year old children
play domino together with a robot, the robot seems to be more engaging when it
shows some misbehaviour compared to when it always behaves as expected
(notwithstanding the likely impact of a novelty effect).

Regarding the design of our three conditions (\emph{lost},
\emph{disobey}, \emph{mistake}), we cannot conclusively affirm whether children perceived the
unexpected robot behaviour as a malfunction (something that happens to a
machine) or as being intended and based on a motivation (something related to a
social entity). Children stated both, when asked why the robot had misbehaved.
Some referred to \textit{``a technical problem''} while others said the robot
\textit{``is tired''} or it \textit{``doesn't want to carry domino tiles any
more but rather go on a tour outside''}. While our manipulations were not as
clearly designed as we expected for the age range of the subjects, we still
believe these three conditions (mechanical malfunction -- the \emph{lost}
condition, vs. explicit intentionality -- the \emph{disobey} condition, vs.
implicit intentionality -- the \emph{mistake} condition) are relevant and we
suggest to replicate a similar study with slightly older children.

%It also appears
%From what we
%have seen in the Domino Study, we have a rough estimate of how children react
%and relate to a robot that behaves unexpectedly from time to time. They are
%mostly surprised, laugh at the robot, and they tend to be more engaged and
%playful. However, they are also confused and cannot really make sense of the
%robot's strange behaviour. We also cannot conclusively tell apart whether children perceived
%the unexpected robot behaviour entirely as a malfunction (something that happens
%to a machine) or as being intended and based on a motivation (something related
%to a social entity). Children stated both, when asked why the robot had
%misbehaved. Some referred to \textit{``a technical problem''} while others said
%the robot \textit{``is tired''} or it \textit{``doesn't want to carry domino
%tiles any more but rather go on a tour outside''}. Maybe our manipulations were
%not as clearly designed as we expected. There is always some freedom in how
%things are interpreted -- especially with young children.  Certainly more work
%needs to be done to investigate which robot behaviour is most beneficial for
%young children and can promote their engagement and motivation to interact with
%Ranger over extended periods of time.

@@

%\subsection{Limitations}
%
%This study and the results have several limitations.  First, we did not have a
%real control group in which the robot always behaved correctly. Instead, we took
%the first interaction phase as a reference for how children interact with the
%correctly behaving robot.  Also, the sample size of 13 groups was small. There
%were  variations in the data due to the individual differences of children. More
%data could have allowed for a better comparison between the conditions.
%
%With the manipulation of the robot behaviour we were able to surprise children.
%However, it is questionable how often the same type of behaviour manipulation
%leads to surprise. Moreover, our experiment was a short-term interaction study
%while we try to make statements about how to sustain long-term engagement. This
%is critical but not unusual. Long-term HRI studies with young children are
%extremely rare as they are difficult to set up as well as time and resource
%consuming \cite{leite_long-term_2013}. Nevertheless, we could have probably
%improved our study by setting up several short interaction sessions spreading
%over several weeks. At the end of each session we could have asked whether
%children want to play again with the robot. Such a study could have helped to
%investigate the long-term interaction with the robot and the impact of the
%behavioural variances.
%
%\subsection{Lessons Learned}
%
%One of the lessons learned is that it is difficult to set up a controlled lab
%study with young children. Children are not like adults who patiently
%participate in a 45-minutes experiment and then get some reward in the end. On
%one hand, an experiment with children should not be boring for them, but on the
%other hand, you would like to seriously collect some data. A lot of the
%challenges we experienced are also described in \cite{ros_child-robot_2011}. One
%of the most difficult parts turned out to be the interviews with the children.
%We need to be careful to not over interpret some of their answers. Some children
%seem to not have a clear opinion and partly contradict themselves. These answers
%are not easy to interpret. An interview script including the questions need to
%be designed very carefully, and should definitely be tested beforehand with the
%respective age group.
%
%Overall, it appears that when trying to study something in more detail, such as
%the manipulation of robot behaviour, 4-5 year old children may be too young. But
%when trying to evaluate a more general approach, the design of a prototype, or
%an interaction scenario, children are a very good choice. They say things as
%they are and react very naturally, when compared to adults, who may reply more
%socially desired. 
%
%
%\paragraph{Summary}

%In this study, we investigated the effect of unexpected robot behaviour on
%children's engagement in interacting with Ranger and on their perception of the
%robot.  Our first hypothesis finds support: children show more engagement toward
%a robot that behaves unexpectedly from time to time. Further, different types of
%unexpected behaviour may have a different effect, and therefore the behaviour
%manipulation needs to be designed with care.

Still, we did not find support for our second hypothesis which stated that children
perceive a robot showing intention or cognitive abilities as more human-like
than a robot that appears to have a system error. While this may be due to the study
setup and the fact that children did not interpret the robot misbehaviour in the
conceived way, our findings seem to suggest the contrary to our hypothesis. A
robot that appeared to do a \textit{mistake} or to be \textit{lost} was more
anthropomorphized than a robot that \textit{disobeyed}.

Another outcome of this study is the initial application of an
anthropomorphism index to a child-robot interaction study. This index
considers both behavioural and phenomenological aspects and is able to indicate
lower and higher levels of anthropomorphism along this continuous index.  Our
experience with this index suggests that children tend to conditionally
anthropomorphize the robot. Higher indexes of anthropomorphism were found in the
\textit{lost} and \textit{mistake} condition which was against our hypothesis.

Interestingly, data suggests a significant negative correlation of engagement
and anthropomorphism index. It appears that groups who interacted more with the
robot perceived it as less-humanlike. This raises an important question for the
human-robot interaction community: to what extent anthropomorphic perceptions
impact the interaction experience. Our findings here go against the intuition.
